\documentclass[12pt]{article}
\usepackage[english]{babel}
\usepackage{cmbright}
\usepackage{enumitem}
\usepackage{fancyhdr}
\usepackage{fontawesome5}
\usepackage{geometry}
\usepackage{hyperref}
\usepackage[sf]{libertine}
\usepackage{microtype}
\usepackage{paracol}
\usepackage{supertabular}
\usepackage{titlesec}
\hypersetup{colorlinks, urlcolor=black, linkcolor=black}

% Geometry
\geometry{hmargin=1.75cm, vmargin=2.5cm}
\columnratio{0.65, 0.35}
\setlength\columnsep{0.05\textwidth}
\setlength\parindent{0pt}
\setlength{\smallskipamount}{8pt plus 3pt minus 3pt}
\setlength{\medskipamount}{16pt plus 6pt minus 6pt}
\setlength{\bigskipamount}{24pt plus 8pt minus 8pt}

% Style
\pagestyle{empty}
\titleformat{\section}{\scshape\LARGE\raggedright}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{\bigskipamount}{\smallskipamount}
\newcommand{\heading}[2]{\centering{\sffamily\Huge #1}\\\smallskip{\large{#2}}}
\newcommand{\entry}[4]{{{\textbf{#1}}} \hfill #3 \\ #2 \hfill #4}
\newcommand{\tableentry}[3]{\textsc{#1} & #2\expandafter\ifstrequal\expandafter{#3}{}{\\}{\\[6pt]}}

\begin{document}

\vspace*{\fill}

\begin{paracol}{2}

% Name & headline
\heading{Harshit sinha}{Self-motivated University student, \\ with a critical experience in learning.}

\switchcolumn

% Identity card
\vspace{0.01\textheight}
\begin{supertabular}{ll}
  \footnotesize\faPhone & +91 9304602588 \\
  \footnotesize\faEnvelope & \href{mailto:john.doe@gmail.com}{harshitsinha49@gmail.com} \\
  \footnotesize\faLinkedin & \href{https://www.linkedin.com/in/harshit-sinha-345614255/}{www.linkedin.com/in/Harshit-sinha} \\
\end{supertabular}

\bigskip
\switchcolumn*

\section{education}

\entry{Batchlor of Technology}{KIIT Deemed To Be University}{9.33 CGPA}{2021 -- Present}
\begin{itemize}[noitemsep,leftmargin=3.5mm,rightmargin=0mm,topsep=6pt]
  \item Database Management System, Operating Systems
  \item Computer Organization and Architecture
  \item DSA, OOPs
\end{itemize}

\medskip

\entry{Class 12th}{Grizzly Vidyalaya}{93.33\%}{2018 -- 2020}

\switchcolumn

\section{skills}
\begin{supertabular}{rl}
  \tableentry{\footnotesize\faCode}{C/C++ \textperiodcentered{} Java \textperiodcentered{} Python}{}
  \tableentry{}{AWS \textperiodcentered{} Git \textperiodcentered{} Machine Learing}{}
  \tableentry{}{Data Structures \textperiodcentered{} Algorithms \textperiodcentered{} OOPs}{}
  \tableentry{}{HTML \textperiodcentered{} CSS \textperiodcentered{} JavaScript}{}
  \tableentry{}{Docker \textperiodcentered{} Boto3 \textperiodcentered{} Kubernetes}{}
  \tableentry{}{}{}

  \tableentry{\footnotesize\faLanguage}{English \textperiodcentered{} proficient}{}
  \tableentry{}{Hindi \textperiodcentered{} native}{}
  \tableentry{}{Japanese \textperiodcentered{} beginner}{}
\end{supertabular}

\switchcolumn*

\section{Projects}

\entry{Cloud Native Monitoring Application}{}{Using AWS}{2023 (1 month)}
\begin{itemize}[noitemsep,leftmargin=3.5mm,rightmargin=0mm,topsep=6pt]
  \item Created a Monitoring App in Python using Flask and psutil.
  \item Containerized the Application using Docker and pushed the Docker Image to ECR using Python Boto3.
  \item Lastly deployed it using Kubernetes.
  \item \href{https://github.com/Harshit-Sinha-49/Cloud-native-monitoring-app}{Cloud Native Monitoring App - Github Link}
\end{itemize}

\medskip

\entry{Spotify clone}{}{Using HTML,CSS,Javascript}{2022}
\begin{itemize}[noitemsep,leftmargin=3.5mm,rightmargin=0mm,topsep=6pt]
  \item Created the fronted using HTML and CSS.
  \item Added the audio playing functionalities using JavaScript.
  \item \href{https://harshit-sinha-49.github.io/Spotify-Clone/}{Spotify clone - Github Link}
\end{itemize}

\medskip

\switchcolumn

\section{other interests}
\begin{supertabular}{rl}
  \tableentry{Indoor}{Sketching \& Painting}{}
  \tableentry{}{Reading}{spaceafter}
  \tableentry{Outdoor}{Cycling}{}
  \tableentry{}{Traveling}{spaceafter}
\end{supertabular}

\bigskip

\section{Certifications}
\begin{supertabular}{rl}
  \tableentry{2023}{\textbf{AWS Cloud Computing}}{}
  \tableentry{}{From Katallyst Consortium Pvt. Ltd.}{spaceafter}
  \tableentry{2022}{\textbf{Supervised Machine Learning}}{}
  \tableentry{}{From Stanford online}{spaceafter}
\end{supertabular}

\end{paracol}

\vspace*{\fill}

\end{document}
